Democracy, Public Support, and Measurement Uncertainty

### 2021-06-15 paper/dcpo_demsupport_appendix.Rmd
add expanded_claassen for ajps and apsr

@@

```{r claassen_replication_input, eval=FALSE}
dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
             ((country=="Albania" & year==1998) |
                (country=="Indonesia" & (year==2001 | year==2006)) |
                (country=="Iran" & year==2000) |
                (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                (country=="Vietnam" & year==2001)) |
             (str_detect(item, "strong_wvs") &
                ((country=="Egypt" & year==2012) |
                   (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                   (country=="India") |
                   (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                   (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                   (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                   (country=="Vietnam" & year==2001))) |
             (country %in% c("Puerto Rico", "Northern Ireland", 
                             "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

claassen_input_cy <- read_csv(here::here("data", "dcpo_input_raw.csv"),
                              col_types = "cdcddcd") %>%           # 1861 obs
  mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
         project = case_when(p_dcpo == "afrob" ~ "afb",
                             p_dcpo == "amb" ~ "lapop",
                             p_dcpo == "arabb" ~ "arb",
                             p_dcpo == "asiab" ~ "asb",
                             p_dcpo == "asianb" ~ "asnb",
                             p_dcpo == "neb" ~ "ndb",
                             p_dcpo == "sasianb" ~ "sab",
                             TRUE ~ p_dcpo),
         y_dcpo = year) %>%
  dplyr::select(country, year, y_dcpo, survey, project) %>% 
  unique()

no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs

@@

available <- anti_join(claassen_input_cy, supdem_cy)                # 564 obs

@@

cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 475 obs
  select(-y_dcpo)

@@

vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

```
\pagebreak

>>>>

vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}
```

@@

```{r claassen_replication_input, eval=FALSE}

# dcpo_input_raw <- DCPOtools::dcpo_setup(vars = read_csv(here::here("data-raw", "mood_dem.csv"),
#                                                         col_types = "cccccc"),
#                                         file = "data/dcpo_input_raw.csv")

dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"), col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
             ((country=="Albania" & year==1998) |
                (country=="Indonesia" & (year==2001 | year==2006)) |
                (country=="Iran" & year==2000) |
                (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                (country=="Vietnam" & year==2001)) |
             (str_detect(item, "strong_wvs") &
                ((country=="Egypt" & year==2012) |
                   (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                   (country=="India") |
                   (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                   (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                   (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                   (country=="Vietnam" & year==2001))) |
             (country %in% c("Puerto Rico", "Northern Ireland", 
                             "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

claassen_input_cy <- read_csv(here::here("data", "dcpo_input_raw.csv"),
                              col_types = "cdcddcd") %>%           # 1864 obs
  mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
         project = case_when(p_dcpo == "afrob" ~ "afb",
                             p_dcpo == "amb" ~ "lapop",
                             p_dcpo == "arabb" ~ "arb",
                             p_dcpo == "asiab" ~ "asb",
                             p_dcpo == "asianb" ~ "asnb",
                             p_dcpo == "neb" ~ "ndb",
                             p_dcpo == "sasianb" ~ "sab",
                             TRUE ~ p_dcpo),
         y_dcpo = year) %>%
  dplyr::select(country, year, y_dcpo, survey, project) %>% 
  unique()

no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1298 obs

@@

available <- anti_join(claassen_input_cy, supdem_cy)                # 566 obs

@@

cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 477 obs
  select(-y_dcpo)

@@

@@

```{r expanded_claassen}
# these are estimates based on Claassen's original dataset, plus all additional country-year-item observations we found; see

load(here::here("data", "exp_claassen_m5_3k_06-13-17-09.rda")) #  dataset of estimates, based on Claassen's original dataset, plus all additional country-year-item observations we found, as generated in (at the moment) expanded_claassen_input.R

exp_claassen_m5_theta <- rstan::extract(exp_claassen_m5, pars = "theta") %>% 
  first()

ls_ec_year <- min(expanded_claassen_input$data$year):max(expanded_claassen_input$data$year)
ls_ec_country <- unique(expanded_claassen_input$data$country)

ec_first_year <- min(expanded_claassen_input$data$year)

ec_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character(),
                                         regime = col_logical())) %>% 
  mutate(country = countrycode::countrycode(as.character(country), "country.name", "country.name"),
         year = as.numeric(as.character(year))) %>% 
  filter(year >= first_year)

# standardize, exactly as in 'supdem stan estimation ajps.R' at L192 (= for assignment and all)
exp_claassen_m5_theta_std = (exp_claassen_m5_theta - mean(as.vector(exp_claassen_m5_theta))) / sd(as.vector(exp_claassen_m5_theta))

ec_df_theta <- purrr::map(1:1000, function(x) {
  exp_claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
    mutate(year = ec_first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(ec_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ec_result_m5_1k <- map(ec_df_theta, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1), model="pooling", data = aDataset)
})

ec_result_betas_m5_1k <- mitools::MIextract(ec_result_m5_1k, fun = coef)
ec_result_vars_m5_1k <- mitools::MIextract(ec_result_m5_1k, fun = vcovBK_se)

ec_df_result_cls_1k <- summary(mitools::MIcombine(results = ec_result_betas_m5_1k, 
                                               variance = ec_result_vars_m5_1k)) %>%
  rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)"))
```

```{r all_claassen_res_ajps_plot, include=TRUE, fig.width=7}
all_claassen_res_ajps <- ec_df_result_cls_1k %>% 
              mutate(model = "Expanded Dataset\nw/ Uncertainty") %>% 
  bind_rows(mod.1_df_result_cls_1k %>% 
              mutate(model = "Claassen w/ Uncertainty")) %>% 
  bind_rows(result_cls[[2]][[1]] %>% 
    mutate(model = "Claassen 2020a",
           term = str_replace(term, "SupDem_trim", "theta_mean"))) %>% 
  filter(!str_detect(term, "(Intercept)"))

all_claassen_res_ajps_plot <- dotwhisker::dwplot(all_claassen_res_ajps) %>% 
  relabel_predictors(c(
    `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
    `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
    `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
    `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
    `plm::lag(theta_mean, 1)` = "Support[t-1]",
    `plm::lag(theta, 1)` = "Support[t-1]",
    `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
    `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
    `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
    `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
    `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
    `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
    `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
    `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
    `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
    `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
    `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
    `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
  )
  ) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  scale_color_discrete(name="Dataset", guide = guide_legend(reverse = TRUE))

all_claassen_res_ajps_plot
```

```{r apsr_1k}
ec_df_theta_apsr <- purrr::map(1:1000, function(x) {
  exp_claassen_m5_theta_std[x,,] %>% 
    as_tibble() %>% 
    rename_with(~ls_ec_country, .cols = starts_with("V")) %>% 
    mutate(year = ec_first_year + row_number() - 1) %>% 
    pivot_longer(cols = !year,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(sd_controls_apsr, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ec_result_m5_1k_apsr <- map(ec_df_theta_apsr, function(aDataset) {
  plm(diff(theta, lag=1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag=1) 
           + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag=1) + plm::lag(lnGDP_imp, 1), 
           aDataset, model="pooling")
})

ec_result_betas_m5_1k_apsr <- mitools::MIextract(ec_result_m5_1k_apsr, fun = coef)
ec_result_vars_m5_1k_apsr <- mitools::MIextract(ec_result_m5_1k_apsr, fun = vcovBK_se)

ec_df_result_cls_1k_apsr <- summary(mitools::MIcombine(results = ec_result_betas_m5_1k_apsr, 
                                                    variance = ec_result_vars_m5_1k_apsr)) %>%
  rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)"))
```

\pagebreak
